---
title: "CNFTSTATS"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    navbar:
      - { title: "Twitter", href: "https://twitter.com/cnftstats"}
      - { title: "About", href: "#about" }
    social: ["menu"]
    css: rmd_flexboard.css
    self_contained: TRUE
    includes:
      in_header: header.html
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, comment = "", dev = "svglite", fig.ext = ".svg")
# Libraries
library(flexdashboard)
library(htmlwidgets)
library(data.table)
library(magrittr)
library(ggplot2)
library(svglite)
library(plotly)
library(DT)

# Data
DT <- readRDS("data/DT.rds")
DTS <- readRDS("data/DTS.rds")
DTE <- readRDS("data/DTE.rds")
RAR <- readRDS("data/RAR.rds")

# javascript (clickable datapoints url)
# https://stackoverflow.com/questions/51681079/how-to-make-scatterplot-points-open-a-hyperlink-using-ggplotly-r
js <- "function(el, x) {
    var id = el.getAttribute('id');
    var gd = document.getElementById(id);
    var d3 = Plotly.d3;
    Plotly.update(id).then(attach);
    function attach() {
        gd.addEventListener('mousemove', function(evt) {
            var xaxis = gd._fullLayout.xaxis;
            var yaxis = gd._fullLayout.yaxis;
            var bb = evt.target.getBoundingClientRect();
            var x = xaxis.p2d(evt.clientX - bb.left);
            x = parseFloat(x).toFixed(0);
            var y = yaxis.p2d(evt.clientY - bb.top);
            y = parseFloat(y).toFixed(0);
            Plotly.relayout(gd, 'xaxis.title', '(' + x + ', ' + y + ')');
        });
    };
    
    el.on('plotly_click', function(d) {
        var link = d.points[0].customdata;
        window.open(link);
    });
    
    document.getElementById('checkbox_map').addEventListener('change', function(event) {
      let map_bg = '';
      if (event.currentTarget.checked) {
        map_bg = 'https://raw.githubusercontent.com' +
                 '/cnftstats/bossplanet/main/' +
                 'map_background_bw.png?raw=true'
        console.log('checked');
      } else {
        map_bg = 'https://raw.githubusercontent.com' +
                 '/cnftstats/bossplanet/main/' +
                 'map_background.png?raw=true'
        console.log('unchecked');
      };
      console.log(map_bg);

      let layout_update = {
        images: [
          {
            source: map_bg,
            xref: 'x',
            yref: 'y',
            x: -180.71,
            y: 179.63,
            sizex: 360.41,
            sizey: 240.26,
            sizing: 'stretch',
            opacity: .4,
            layer: 'below'
          }
        ]
      }
      Plotly.relayout(gd, layout_update);
    });
}"

js2 <- "function(el, x) {
    var id = el.getAttribute('id');
    var gd = document.getElementById(id);
    var d3 = Plotly.d3;
    Plotly.update(id).then(attach);
    function attach() {
        gd.addEventListener('mousemove', function(evt) {
            var xaxis = gd._fullLayout.xaxis;
            var yaxis = gd._fullLayout.yaxis;
            var bb = evt.target.getBoundingClientRect();
            var x = xaxis.p2d(evt.clientX - bb.left);
            x = parseFloat(x).toFixed(0);
            var y = yaxis.p2d(evt.clientY - bb.top);
            y = parseFloat(y).toFixed(0);
            var layout_update = {
              annotations: [
                {
                  x: 0,
                  y: -54,
                  xref: 'x',
                  yref: 'y',
                  text: '(' + x + ', ' + y + ')',
                  showarrow: false,
                  font: {
                    size: 14,
                    color: '#b3b3b3',
                  },
                },
              ]
            }
            Plotly.relayout(gd, layout_update);
        });
    };
    el.on('plotly_click', function(d) {
        var link = d.points[0].customdata;
        window.open(link);
    });
}"


js3 <- "function(el, x) {
    var id = el.getAttribute('id');
    var gd = document.getElementById(id);
    var d3 = Plotly.d3;
    Plotly.update(id).then(attach);
    function attach() {
        gd.addEventListener('mousemove', function(evt) {
            var xaxis = gd._fullLayout.xaxis;
            var yaxis = gd._fullLayout.yaxis;
            var bb = evt.target.getBoundingClientRect();
            var x = xaxis.p2d(evt.clientX - bb.left);
            x = parseFloat(x).toFixed(0);
            var y = yaxis.p2d(evt.clientY - bb.top);
            y = parseFloat(y).toFixed(0);
            Plotly.relayout(gd, 'xaxis.title', 'x: ' + x + '  y: ' + y);
        });
    };
    el.on('plotly_click', function(d) {
        var link = d.points[0].data.customdata[0];
        window.open(link);
    });
}"
```

<!-- Add live timestamp -->
```{r results='asis'}
timestamp <- as.numeric(Sys.time())
cat("
<script>
$(document).ready(function(){
  $('.navbar-author').after('</br><span id=\"updatedat\">Updated: <span data-livestamp=\"", timestamp, "\"></span></span>');
});
</script>
", sep = "")
```


# Sidebar {data-width=80, .sidebar}
<ul id="sidebar_ul">
  <li><a href="https://cnftstats.github.io/adapes">ApeSociety</a></li>
  <li><a href="https://cnftstats.github.io/bcrc">BCRC</a></li>
  <li id="currentProject"><a href="https://cnftstats.github.io/bossplanet">BossPlanet</a></li>
  <li><a href="https://cnftstats.github.io/cabins">Cabins</a></li>
  <li><a href="https://cnftstats.github.io/chilledkongs">ChilledKongs</a></li>
  <li><a href="https://cnftstats.github.io/claynation">Clay Nation</a></li>
  <li><a href="https://cnftstats.github.io/discosolaris">DiscoSolaris</a></li>
  <li><a href="https://cnftstats.github.io/mocossi">Mocossi</a></li>
  <li><a href="https://cnftstats.github.io/pavia">Pavia</a></li>
  <li><a href="https://cnftstats.github.io/spacebudz">SpaceBudz</a></li>
  <li><a href="https://cnftstats.github.io/vox">VoxCats</a></li>
</ul>

# Floor {data-icon="ion-arrow-graph-up-right"}
## Column 1 {data-width=650, .tabset}
### Listings
```{r fig.height=7, fig.width=10}
X <- copy(DT[type != "bundle"])
X[price %between% c(0, 999),     price_range := trunc(price/100)*100]
X[price %between% c(1000, 4999), price_range := trunc(price/1000)*1000]
X[price >= 5000,                 price_range := 5000]
X <- X[complete.cases(price_range), .(price_range, price, market, district_txt)]
CAP <- X[, .(floor = min(price), median = floor(median(price)),
             listings = .N), district_txt][order(district_txt)]
CAP_all <- X[, .(district_txt = "All", floor = min(price),
                 median = floor(median(price)), listings = .N)]
CAP <- rbind(CAP_all, CAP)
.pattern <- "%s: Floor = %d | Median = %d | Listings = %d"
.caption <- paste0(CAP[, sprintf(.pattern, district_txt, floor, median, listings)], collapse = "\n")
X <- X[, .N, .(price_range, market, district_txt)][order(price_range)]
X[price_range %between% c(0, 999),     x_label := paste0(price_range, "-", price_range + (100-1))]
X[price_range %between% c(1000, 4999), x_label := paste0(price_range, "-", price_range + (1000-1))]
X[price_range >= 5000,                 x_label := "5000+"]
.X <- X[, .(price_range, x_label)] %>% unique %>% .[order(price_range)]
X[, x_label := factor(x_label, levels = .X$x_label)]
X[, market  := factor(market, levels = c("jpg.store", "cnft.io"))]
ggplot(X, aes(x_label, N, fill = market)) +
  facet_wrap(.~district_txt, nrow = 3, ncol = 3) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = stat(y), group = x_label),
            stat = 'summary', fun = sum, vjust = -.5, hjust = +.55,
            color = "steelblue4", size = 3) +
  scale_fill_manual(values = c("jpg.store" = "steelblue3", "cnft.io" = "steelblue4")) +
  scale_alpha_manual(values = 0.9, guide = "none") +
  labs(x = "Price range", y = "Number of listings", fill = "", caption = .caption) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = -45, vjust = +.5, hjust = 0,
                                   color = "grey50", size = 8),
        axis.text.y = element_text(color = "grey50", size = 8),
        axis.title = element_text(color = "grey30", size = 10),
        legend.position = "bottom", legend.justification = 'right', legend.direction = "horizontal",
        legend.text = element_text(color = "grey50", size = 9),
        legend.key.height = unit(0.5, "points"), legend.key.width = unit(10, "points"),
        legend.box.spacing = unit(-10, "points"),
        plot.caption = element_text(color = "#008B8B", vjust = +15, hjust = 0, size = 8),
        plot.margin = unit(c(0, 15, 0, 0), units = "pt"),
        panel.grid.minor = element_blank())
```

> The <a href="https://www.mathsisfun.com/median.html" target="_blank">median</a> is the 'middle point' of all the listing.

### Sales (last 24h)
```{r fig.height=7, fig.width=10}
X <- copy(DTS[type != "bundle" & sold_at_hours <= 24])
X[price %between% c(0, 999),     price_range := trunc(price/100)*100]
X[price %between% c(1000, 4999), price_range := trunc(price/1000)*1000]
X[price >= 5000,                 price_range := 5000]
X <- X[complete.cases(price_range), .(price_range, price, market, district_txt)]
CAP <- X[, .(floor = min(price), roof = max(price), sales = .N), district_txt][order(district_txt)]
.caption <- paste0(CAP[, sprintf("%s: Sale floor = %s | Sale roof = %d | Sales = %d",
                                 district_txt, floor, roof, sales)],
                   collapse = "\n")
X <- X[, .N, .(price_range, market, district_txt)][order(price_range)]
X[price_range %between% c(0, 999),     x_label := paste0(price_range, "-", price_range + (100-1))]
X[price_range %between% c(1000, 4999), x_label := paste0(price_range, "-", price_range + (1000-1))]
X[price_range >= 5000,                 x_label := "5000+"]
.X <- X[, .(price_range, x_label)] %>% unique %>% .[order(price_range)]
X[, x_label := factor(x_label, levels = .X$x_label)]
X[, market  := factor(market, levels = c("jpg.store", "cnft.io"))]
ggplot(X, aes(x_label, N, fill = market)) +
  facet_wrap(.~district_txt, nrow = 3, ncol = 3) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = stat(y), group = x_label),
            stat = 'summary', fun = sum, vjust = -.5, hjust = +.55,
            color = "steelblue4", size = 3) +
  scale_fill_manual(values = c("jpg.store" = "springgreen3", "cnft.io" = "springgreen4")) +
  scale_alpha_manual(values = 0.9, guide = "none") +
  labs(x = "Price range", y = "Number of sales", fill = "", caption = .caption) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = -45, vjust = +.5, hjust = 0,
                                   color = "grey50", size = 8),
        axis.text.y = element_text(color = "grey50", size = 8),
        axis.title = element_text(color = "grey30", size = 10),
        legend.position = "bottom", legend.justification = 'right', legend.direction = "horizontal",
        legend.text = element_text(color = "grey50", size = 9),
        legend.key.height = unit(0.5, "points"), legend.key.width = unit(10, "points"),
        legend.box.spacing = unit(-10, "points"),
        plot.caption = element_text(color = "#008B8B", vjust = +15, hjust = 0, size = 8),
        plot.margin = unit(c(0, 15, 0, 0), units = "pt"),
        panel.grid.minor = element_blank())
```

> Warning: Only last 72h sales are included. `Bundles` (multiple assets sold together) are excluded!

## Column 2 {data-width=350}
### Sweep that floor: Lowest listings
```{r}
X <- DT[order(price)][1:30]
X[, asset := sprintf("<a href='%s' target='_blank'>%s</a>", link, asset)]
X <- X[, .(asset, price, district, market)]
X <- X[complete.cases(X)]
datatable(X, class = 'compact stripe hover nowrap',
          options = list(dom = "t",
                         pageLength = 100,
                         scrollY = '100%',
                         bLengthChange = FALSE,
                         bPaginate = FALSE,
                         info = FALSE,
                         columnDefs = list(list(className = 'dt-right', targets = "_all"))),
          colnames = c("Asset", "Price", "District", "Market"),
          rownames = FALSE,
          escape = FALSE) %>%
  formatStyle(columns = 1:ncol(X), fontSize = '90%')
```

# Map {data-icon="ion-android-map"}
## Column 1 {.tabset}

<!-- ### Tiles -->
<!-- ```{r} -->
<!-- # XRAR <- RAR[!asset %in% DT$asset] -->
<!-- map_background <- paste0("https://raw.githubusercontent.com/cnftstats/bossplanet/", -->
<!--                          "main/map_background.png?raw=true") -->


<!-- X <- data.table(expand.grid(x = -180:180, y = -60:180), -->
<!--                 price_rank = as.numeric(NA), link = NA, text_tooltip = "HI") -->
<!-- X[, xy := paste(x, y, sep = ",")] -->
<!-- setnames(X, c("x", "y"), c("xcoord", "ycoord")) -->

<!-- Y <- copy(DT) -->
<!-- Y[, xy := paste(xcoord, ycoord, sep = ",")] -->
<!-- Y[, text_tooltip := sprintf("%s</br></br>Price: %.0f</br>District: %.0f</br>Type: %s</br>Market: %s", -->
<!--                             asset, price, district, type, market)] -->
<!-- Y <- Y[, .(xcoord, ycoord, price_rank, link, text_tooltip, xy)] -->

<!-- X <- X[!xy %in% Y$xy] -->
<!-- X <- rbindlist(list(X, Y), use.names = TRUE) -->

<!-- # loj(X, DT[, .(xcoord, ycoord, price_rank, link, xy)], "xy") -->

<!-- gg <- ggplot(X, customdata = link, text = text_tooltip) + -->
<!--   geom_tile(aes(xcoord, ycoord, fill = price_rank)) + -->
<!--   scale_x_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) + -->
<!--   scale_y_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) + -->
<!--   scale_fill_gradient2(low = 'steelblue3', mid = "goldenrod1", midpoint = .5, high = 'red', -->
<!--                         na.value = "grey90", -->
<!--                         breaks = 0:1, labels = c("Low", "High"), limits = 0:1) + -->
<!--   labs(color = "Price", x = "", y = "") + -->
<!--   theme(panel.grid.minor = element_blank(), -->
<!--         panel.grid.major = element_line(colour = "grey80"), -->
<!--         panel.background = element_rect(fill = 'transparent')) -->

<!-- ggplotly(gg, tooltip = "text") %>% config(scrollZoom = TRUE) %>% onRender(js3) -->
<!-- ``` -->


<!-- ### Listings plotly -->
<!-- ```{r} -->
<!-- map_background <- paste0("https://raw.githubusercontent.com/cnftstats/bossplanet/", -->
<!--                          "main/map_background.png?raw=true") -->

<!-- # To do: -->
<!-- # add_polygons (so can be zoomed) -->
<!-- # hoverlabel background incorrect color! -->


<!-- X <- copy(DT) -->

<!-- percent_high_low <- 15 -->

<!-- .lowest_prices <- DT$price[order(DT$price)] -->
<!-- .lowest_prices <- .lowest_prices[1:(floor(length(.lowest_prices)*percent_high_low/100))] -->
<!-- .lowest_prices <- max(.lowest_prices) -->

<!-- .highest_prices <- DT$price[order(-DT$price)] -->
<!-- .highest_prices <- .highest_prices[1:(floor(length(.highest_prices)*percent_high_low/100))] -->
<!-- .highest_prices <- min(.highest_prices) -->

<!-- X[, pricelvl := fcase(price <= .lowest_prices, "Low", -->
<!--                       price > .lowest_prices & price < .highest_prices, "Med", -->
<!--                       price >= .highest_prices, "High")] -->
<!-- X[, pricelvl := factor(pricelvl, levels = c("Low", "Med", "High"))] -->

<!-- X[, type := factor(type, levels = c("listing", "bundle"), -->
<!--                    labels = c("listing" = "Listing", "bundle" = "Bundle"))] -->

<!-- X[, type_pricelvl := factor(paste0(type, "-", pricelvl), -->
<!--                             levels = c("Listing-Low", "Listing-Med", "Listing-High", -->
<!--                                        "Bundle-Low", "Bundle-Med", "Bundle-High"))] -->

<!-- # Fix hoverlabel bgcolor (not working with WebGL) -->
<!-- X <- X[order(type_pricelvl)] -->
<!-- length_unique_vals <- length(unique(X$price)) -->
<!-- .colors <- colorRampPalette(c('#0d71db', "#dbc00d", "#db220d"))(length_unique_vals) -->
<!-- .colors <- .colors[factor(X$price)] -->
<!-- X[, price_color := .colors] -->

<!-- plot_ly( -->
<!--   data = X, x = ~xcoord, y = ~ycoord, -->
<!--   type = "scattergl", mode = "markers", -->
<!--   split = ~type_pricelvl, -->
<!--   customdata = ~link, -->
<!--   text = ~paste0("</br>(", xcoord, ", ", ycoord, ")", -->
<!--                  "</br>", round(price, 2), " ada", -->
<!--                  "</br>D", district, -->
<!--                  "</br>", type, -->
<!--                  "</br>", market), -->
<!--   hoverinfo = "text", -->
<!--   hoverlabel = list(bgcolor = .colors), -->
<!--   color = ~price_rank, -->
<!--   colors = c('#0d71db', "#dbc00d", "#db220d"), -->
<!--   marker = list( -->
<!--     size = 3 -->
<!--   )) %>% -->
<!--   colorbar( -->
<!--     title = list(text = "Price"), -->
<!--     len = .35, # length of the color bar -->
<!--     x = 1, -->
<!--     y = 1, -->
<!--     outlinewidth = .5, -->
<!--     thickness = 15, -->
<!--     tickmode = "array", -->
<!--     tickvals = c(0, 1), -->
<!--     ticktext = c("Low", "High") -->
<!--   ) %>% -->
<!--   layout( -->
<!--     title = "", -->
<!--     xaxis = list( -->
<!--       title = list(text = ""), -->
<!--       range = c(0, 1), -->
<!--       tickmode = "array", -->
<!--       tickvals = c(-180, -60, 60, 180), -->
<!--       ticktext = c("-180", "-60", "60", "180"), -->
<!--       color = "#b3b3b3", -->
<!--       gridcolor = "#cfcfcf", -->
<!--       layer = "above traces", -->
<!--       showline = FALSE, -->
<!--       ticklabelposition = "outside", -->
<!--       ticklen = 4, -->
<!--       zeroline = FALSE -->
<!--     ), -->
<!--     yaxis = list( -->
<!--       title = list(text = ""), -->
<!--       range = c(-61, 181), -->
<!--       tickmode = "array", -->
<!--       tickvals = c(-60, 60, 180), -->
<!--       ticktext = c("-60", "60", "180"), -->
<!--       color = "#b3b3b3", -->
<!--       gridcolor = "#cfcfcf", -->
<!--       layer = "above traces", -->
<!--       showline = FALSE, -->
<!--       ticklabelposition = "outside", -->
<!--       ticklen = 4, -->
<!--       zeroline = FALSE, -->
<!--       scaleanchor = "x", # to fix scale ratio so it is square -->
<!--       scaleratio = 1 # to fix scale ratio so it is square -->
<!--     ), -->
<!--     font = list( -->
<!--       color = "grey", -->
<!--       size = 11 -->
<!--     ), -->
<!--     legend = list( -->
<!--       x = 1, -->
<!--       y = .4, -->
<!--       title = list(text = "Type"), -->
<!--       font = list(size = 9) -->
<!--     ), -->
<!--     images = list(list( -->
<!--       source = map_background, -->
<!--       xref = "x", -->
<!--       yref = "y", -->
<!--       x = -183.5, -->
<!--       y = 181.3, -->
<!--       sizex = 366.1, -->
<!--       sizey = 243.7, -->
<!--       sizing = "stretch", -->
<!--       opacity = .5, -->
<!--       layer = "below" -->
<!--     )), -->
<!--     margin = list( -->
<!--       autoexpand = TRUE, -->
<!--       pad = 0, -->
<!--       t = 15, -->
<!--       # r = 100, -->
<!--       # b = 30, -->
<!--       l = 100 -->
<!--     ) -->
<!--   ) %>% -->
<!--   config(scrollZoom = TRUE, displaylogo = FALSE) %>% -->
<!--   onRender(js2) %>% -->
<!--   toWebGL() %>% partial_bundle(local = FALSE) -->
<!-- ``` -->


### Listings
```{r}
map_background <- paste0("https://raw.githubusercontent.com/cnftstats/bossplanet/",
                         "main/map_background.png?raw=true")

X <- copy(DT)

percent_high_low <- 15

.lowest_prices <- DT$price[order(DT$price)]
.lowest_prices <- .lowest_prices[1:(floor(length(.lowest_prices)*percent_high_low/100))]
.lowest_prices <- max(.lowest_prices)

.highest_prices <- DT$price[order(-DT$price)]
.highest_prices <- .highest_prices[1:(floor(length(.highest_prices)*percent_high_low/100))]
.highest_prices <- min(.highest_prices)

X[, show_price := fcase(price <= .lowest_prices, "Low",
                        price > .lowest_prices & price < .highest_prices, "Med",
                        price >= .highest_prices, "High")]
X[, show_price := factor(show_price, levels = c("Low", "Med", "High"))]

X[, type := factor(type, levels = c("listing", "bundle"), labels = c("Listing", "Bundle"))]

gg <- ggplot() +
  geom_point(data = X, 
             aes(x = xcoord, y = ycoord, color = price_rank, shape = type, customdata = link,
                 alpha = show_price,
                 text = paste0("(", xcoord, ", ", ycoord, ")",
                               "</br></br>", paste0(round(price, 2), " ada",
                                                    "</br>D", district,
                                                    "</br>", type,
                                                    "</br>", market))), size = .6) +
  scale_color_gradient2(low = 'steelblue3', mid = "goldenrod1", midpoint = .5, high = 'red',
                        na.value = "grey90",
                        breaks = 0:1, labels = c("Low", "High"), limits = 0:1) +
  scale_x_continuous(expand = c(0.0005, 0.0005)) +
  scale_y_continuous(expand = c(0.0005, 0.0005)) +
  scale_shape_manual(name = "Filter", values = c("Listing" = 16, "Bundle" = 17)) +
  scale_alpha_manual(name = " ", values = rep(1, length(unique(X$show_price)))) +
  labs(color = "Price", x = "", y = "") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.background = element_rect(fill = 'transparent'),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title.x = element_text(size = 11, color = "grey40"),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 9, color = "grey40")) +
  coord_fixed(xlim = c(-181, 180), ylim = c(-61, 180))

ggplotly(gg, type = 'scattergl', tooltip = "text") %>%
  layout(
    xaxis = list(range = c(0, 1)),
    legend = list(x = 1, y = .4, bgcolor = 'rgba(255,255,255,0.6)'),
    hoverdistance = 10,
    images = list(list(
      source = map_background,
      xref = "x",
      yref = "y",
      x = -180.71,
      y = 179.63,
      sizex = 360.41,
      sizey = 240.26,
      sizing = "stretch",
      opacity = .4,
      layer = "below"
    ))
  ) %>%
  config(scrollZoom = TRUE, displaylogo = FALSE) %>% 
  onRender(js) %>% toWebGL() %>% partial_bundle(local = FALSE)
```

<div id="checkbox_map_div">
  <input type="checkbox" id="checkbox_map" name="checkbox_map">
  <label for="checkbox_map" id="checkbox_map_label"> B&W map</label>
</div>

> Click on the data points to open the listings. Zoom-in/out with your mouse wheel. <b><span style='color:red'>Double click on the `(Listing,Low)` legend to display only the lowest listings.</span></b>



### Sales (last 24h)
```{r}
X <- DTS[sold_at_hours <= 24]
X[, sold_time := sprintf("%.fh ago", sold_at_hours)]

X[, type := factor(type, levels = c("listing", "bundle"), labels = c("Listing", "Bundle"))]

gg <- ggplot() +
  geom_point(data = X, 
             aes(x = xcoord, y = ycoord, color = price_rank, shape = type,
                 text = paste0("(", xcoord, ", ", ycoord, ")",
                               "</br></br>", paste0(round(price, 2), " ada",
                                                    "</br>D", district,
                                                    "</br>", type,
                                                    "</br>", sold_time,
                                                    "</br>", market))), size = .6) +
  scale_color_gradient2(low = 'steelblue3', mid = "goldenrod1", midpoint = .5, high = 'red',
                        na.value = "grey90",
                        breaks = 0:1, labels = c("Low", "High"), limits = 0:1) +
  scale_x_continuous(expand = c(0.0005, 0.0005)) +
  scale_y_continuous(expand = c(0.0005, 0.0005)) +
  scale_shape_manual(name = "Filter", values = c("Listing" = 16, "Bundle" = 17)) +
  labs(color = "Price", x = "", y = "") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        panel.background = element_rect(fill = 'transparent'),
        axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title.x = element_text(size = 11, color = "grey40"),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 9, color = "grey40")) +
  coord_fixed(xlim = c(-181, 180), ylim = c(-61, 180))

ggplotly(gg, type = 'scattergl', tooltip = "text") %>%
  layout(
    xaxis = list(range = c(0, 1)),
    legend = list(x = 1, y = .4, bgcolor = 'rgba(255,255,255,0.6)'),
    hoverdistance = 10,
    images = list(list(
      source = map_background,
      xref = "x",
      yref = "y",
      x = -180.71,
      y = 179.63,
      sizex = 360.41,
      sizey = 240.26,
      sizing = "stretch",
      opacity = .4,
      layer = "below"
    ))
  ) %>%
  config(scrollZoom = TRUE, displaylogo = FALSE) %>% 
  onRender(js) %>% toWebGL() %>% partial_bundle(local = FALSE)
```

> Click and drag your mouse to zoom. You can zoom-in/out with your mouse wheel. Grey areas are minted lands. I have no clue what the white areas are.

<!-- ### Plot lands -->
<!-- <iframe src="https://cnftstats.github.io/bossplanet/plot_lands" style="height:100%;width:100%;border:none;" title="plot_lands"></iframe> -->

### Minted
```{r fig.height=10}
CAP <- RAR[, .(minted = .N, percent = sprintf("%05.02f%%", .N/nrow(RAR)*100)), district]
CAP <- CAP[, sprintf("District %s = %d (%s) lands", district, minted, percent)]
CAP <- paste0(CAP, collapse = "\n")
CAP <- paste0("Total = ", nrow(RAR), " (100%) lands\n", CAP)
cat(CAP)


# ggplot(RAR, aes(x = xcoord, y = ycoord)) +
#   geom_point(color = "grey60", size = .3) +
#   scale_x_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) +
#   scale_y_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) +
#   labs(x = "", y = "", title = "Boss Planet minted lands", subtitle = CAP) +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_line(colour = "grey80"),
#         panel.background = element_rect(fill = 'transparent'),
#         plot.title = element_text(color = "firebrick4", size = 15),
#         plot.subtitle = element_text(color = "steelblue3", size = 12)) +
#   coord_fixed(xlim = c(-180, 180), ylim = c(-180, 180), expand = TRUE)
```


# Buy me a coffee {data-icon="ion-coffee"}
## Column 1
### Thanks for your support!
Tips would be greatly appreciated! This would encourage me to maintain and improve the website (for instance, to get a better hosting service).  

![Tip me](tipme.svg){width=200px}  
**addr1qx04gwr9kazlpnm6t8a8h0pggk440zs3fdayct732a0wwwd3usryhnh52pevj5xy7cgp9d4jnywar6g0tnct58dyfukszl25n8** 

# about {.hidden}
## Columun 1
### About the website
#### The data
- Listings data is comes from <a href="https://cnft.io/" target="_blank">cnft.io</a>, <a href="https://www.jpg.store/" target="_blank">jpg.store</a>and <a href="https://www.spacebudz.io/" target="_blank">spacebudz.io</a> marketplaces
- Rank and rarity scores come from <a href="https://cnft.tools/" target="_blank">cnft.tools</a>.
- The website is updated every ~10mins. You need to hit `F5` to manually see the updates on the website.

#### Disclaimer
- This is an early version, so there might be some bugs! Use at your own risk

## Columun 2
### Other useful websites
#### Official websites
- <a href="https://bosscatrocketclub.com/" target="_blank">bosscatrocketclub.com</a>
- <a href="https://chilledkongs.com/" target="_blank">chilledkongs.com</a>
- <a href="https://mocossi.com/" target="_blank">mocossi.com</a>
- <a href="https://spaceapeclub.io/" target="_blank">spaceapeclub.io</a>
- <a href="https://www.pavia.io/" target="_blank">pavia.io</a>

#### General tools
- <a href="https://opencnft.io/" target="_blank">opencnft.io</a>
- <a href="https://cnft.tools/" target="_blank">cnft.tools</a>
- <a href="https://www.cnftjungle.io/" target="_blank">cnftjungle.io</a>
- <a href="https://www.belowfloor.io/" target="_blank">belowfloor.io</a>

#### Specific tools
- <a href="https://pavia.3dkiwi.io/" target="_blank">Pavia heatmap</a>


## Column 3
### About me
- I am passionate about crypto, (c)nfts, stats, and programming!
- Hit me on discord: <a href="https://discord.com/users/K2#8332/" target="_blank">K2#8332</a>
- Follow me on Twitter: <a href="https://twitter.com/cnftstats" target="_blank">@cnftstats</a>


<!-- https://ionic.io/ionicons/v2/cheatsheet.html -->
<!-- https://www.qrcode-monkey.com/#text -->
