---
title: "Boss Planet Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    navbar:
      - { title: "Twitter", href: "https://twitter.com/cnftstats"}
      - { title: "About", href: "#about" }
    social: ["menu"]
    css: rmd_flexboard.css
    self_contained: TRUE
    includes:
      in_header: header.html
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, comment = "", dev = "svglite", fig.ext = ".svg")
# Libraries
library(flexdashboard)
library(htmlwidgets)
library(data.table)
library(magrittr)
library(ggplot2)
library(svglite)
library(plotly)
library(DT)

# Data
DT <- readRDS("data/DT.rds")
DTS <- readRDS("data/DTS.rds")
DTE <- readRDS("data/DTE.rds")
RAR <- readRDS("data/RAR.rds")

# javascript (clickable datapoints url)
# https://stackoverflow.com/questions/51681079/how-to-make-scatterplot-points-open-a-hyperlink-using-ggplotly-r
js <- "function(el, x) {
    var id = el.getAttribute('id');
    var gd = document.getElementById(id);
    var d3 = Plotly.d3;
    Plotly.update(id).then(attach);
    function attach() {
        gd.addEventListener('mousemove', function(evt) {
            var xaxis = gd._fullLayout.xaxis;
            var yaxis = gd._fullLayout.yaxis;
            var bb = evt.target.getBoundingClientRect();
            var x = xaxis.p2d(evt.clientX - bb.left);
            x = parseFloat(x).toFixed(0);
            var y = yaxis.p2d(evt.clientY - bb.top);
            y = parseFloat(y).toFixed(0);
            Plotly.relayout(gd, 'xaxis.title', 'x: ' + x + '  y: ' + y);
        });
    };
    el.on('plotly_click', function(d) {
        var link = d.points[0].customdata;
        window.open(link);
    });
}"


# Functions
loj <- function (X = NULL, Y = NULL, onCol = NULL) {
  if (truelength(X) == 0 | truelength(Y) == 0) 
    stop("setDT(X) and setDT(Y) first")
  n <- names(Y)
  X[Y, `:=`((n), mget(paste0("i.", n))), on = onCol]
}
```

<!-- Add live timestamp -->
```{r results='asis'}
timestamp <- as.numeric(Sys.time())
cat("
<script>
$(document).ready(function(){
  $('.navbar-author').after('</br><span id=", '"updatedat"', ">Updated: <span data-livestamp=", '"', timestamp, '"', "></span></span>');
});
</script>
", sep = "")
```

# Sidebar {data-width=80, .sidebar}
<ul id="sidebar_ul">
<li><a href="https://cnftstats.github.io/adapes">ApesSociety</a></li>
<li><a href="https://cnftstats.github.io/bcrc">BCRC</a></li>
<li><a href="https://cnftstats.github.io/borgs">BorgsClub</a></li>
<li id="currentProject"><a href="https://cnftstats.github.io/bossplanet">BossPlanet</a></li>
<li><a href="https://cnftstats.github.io/chilledkongs">ChilledKongs</a></li>
<li><a href="https://cnftstats.github.io/claynation">Clay Nation</a></li>
<li><a href="https://cnftstats.github.io/discosolaris">DiscoSolaris</a></li>
<li><a href="https://cnftstats.github.io/mocossi">Mocossi</a></li>
<li><a href="https://cnftstats.github.io/pavia">Pavia</a></li>
<li><a href="https://cnftstats.github.io/spacebudz">SpaceBudz</a></li>
</ul>

# Floor {data-icon="ion-arrow-graph-up-right"}
## Column 1 {data-width=650, .tabset}
### Listings
```{r fig.height=7, fig.width=10}
X <- copy(DT[type != "bundle"])
X[price %between% c(0, 999),     price_range := trunc(price/100)*100]
X[price %between% c(1000, 4999), price_range := trunc(price/1000)*1000]
X[price >= 5000,                 price_range := 5000]
X <- X[complete.cases(price_range), .(price_range, price, market, district_txt)]
CAP <- X[, .(floor = min(price), listings = .N), district_txt][order(district_txt)]
.caption <- paste0(CAP[, sprintf("%s: Floor = %s | Listings = %d", district_txt, floor, listings)],
                   collapse = "\n")
X <- X[, .N, .(price_range, market, district_txt)][order(price_range)]
X[price_range %between% c(0, 999),     x_label := paste0(price_range, "-", price_range + (100-1))]
X[price_range %between% c(1000, 4999), x_label := paste0(price_range, "-", price_range + (1000-1))]
X[price_range >= 5000,                 x_label := "5000+"]
.X <- X[, .(price_range, x_label)] %>% unique %>% .[order(price_range)]
X[, x_label := factor(x_label, levels = .X$x_label)]
X[, market  := factor(market, levels = c("jpg.store", "cnft.io"))]
ggplot(X, aes(x_label, N, fill = market)) +
  facet_wrap(.~district_txt, nrow = 3, ncol = 3) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = stat(y), group = x_label),
            stat = 'summary', fun = sum, vjust = -.5, hjust = +.55,
            color = "steelblue4", size = 3) +
  scale_fill_manual(values = c("jpg.store" = "steelblue3", "cnft.io" = "steelblue4")) +
  scale_alpha_manual(values = 0.9, guide = "none") +
  labs(x = "Price range", y = "Number of listings", fill = "", caption = .caption) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = -45, vjust = +.5, hjust = 0,
                                   color = "grey50", size = 8),
        axis.text.y = element_text(color = "grey50", size = 8),
        axis.title = element_text(color = "grey30", size = 10),
        legend.position = "bottom", legend.justification = 'right', legend.direction = "horizontal",
        legend.text = element_text(color = "grey50", size = 9),
        legend.key.height = unit(0.5, "points"), legend.key.width = unit(10, "points"),
        legend.box.spacing = unit(-10, "points"),
        plot.caption = element_text(color = "#008B8B", vjust = +15, hjust = 0, size = 8),
        plot.margin = unit(c(0, 15, 0, 0), units = "pt"),
        panel.grid.minor = element_blank())
```

> Warning: `Bundles` (multiple assets listed together) are excluded!

### Sales (last 24h)
```{r fig.height=7, fig.width=10}
X <- copy(DTS[type != "bundle" & sold_at_hours <= 24])
X[price %between% c(0, 999),     price_range := trunc(price/100)*100]
X[price %between% c(1000, 4999), price_range := trunc(price/1000)*1000]
X[price >= 5000,                 price_range := 5000]
X <- X[complete.cases(price_range), .(price_range, price, market, district_txt)]
CAP <- X[, .(floor = min(price), roof = max(price), sales = .N), district_txt][order(district_txt)]
.caption <- paste0(CAP[, sprintf("%s: Sale floor = %s | Sale roof = %d | Sales = %d",
                                 district_txt, floor, roof, sales)],
                   collapse = "\n")
X <- X[, .N, .(price_range, market, district_txt)][order(price_range)]
X[price_range %between% c(0, 999),     x_label := paste0(price_range, "-", price_range + (100-1))]
X[price_range %between% c(1000, 4999), x_label := paste0(price_range, "-", price_range + (1000-1))]
X[price_range >= 5000,                 x_label := "5000+"]
.X <- X[, .(price_range, x_label)] %>% unique %>% .[order(price_range)]
X[, x_label := factor(x_label, levels = .X$x_label)]
X[, market  := factor(market, levels = c("jpg.store", "cnft.io"))]
ggplot(X, aes(x_label, N, fill = market)) +
  facet_wrap(.~district_txt, nrow = 3, ncol = 3) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = stat(y), group = x_label),
            stat = 'summary', fun = sum, vjust = -.5, hjust = +.55,
            color = "steelblue4", size = 3) +
  scale_fill_manual(values = c("jpg.store" = "springgreen3", "cnft.io" = "springgreen4")) +
  scale_alpha_manual(values = 0.9, guide = "none") +
  labs(x = "Price range", y = "Number of sales", fill = "", caption = .caption) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = -45, vjust = +.5, hjust = 0,
                                   color = "grey50", size = 8),
        axis.text.y = element_text(color = "grey50", size = 8),
        axis.title = element_text(color = "grey30", size = 10),
        legend.position = "bottom", legend.justification = 'right', legend.direction = "horizontal",
        legend.text = element_text(color = "grey50", size = 9),
        legend.key.height = unit(0.5, "points"), legend.key.width = unit(10, "points"),
        legend.box.spacing = unit(-10, "points"),
        plot.caption = element_text(color = "#008B8B", vjust = +15, hjust = 0, size = 8),
        plot.margin = unit(c(0, 15, 0, 0), units = "pt"),
        panel.grid.minor = element_blank())
```

> Warning: Only last 72h sales are included. `Bundles` (multiple assets sold together) are excluded!

## Column 2 {data-width=350}
### Sweep that floor: Lowest listings
```{r}
X <- DT[order(price)][1:30]
X[, asset := sprintf("<a href='%s' target='_blank'>%s</a>", link, asset)]
X <- X[, .(asset, price, district, market)]
X <- X[complete.cases(X)]
datatable(X, class = 'compact stripe hover nowrap',
          options = list(dom = "t",
                         pageLength = 100,
                         scrollY = '100%',
                         bLengthChange = FALSE,
                         bPaginate = FALSE,
                         info = FALSE,
                         columnDefs = list(list(className = 'dt-right', targets = "_all"))),
          colnames = c("Asset", "Price", "District", "Market"),
          rownames = FALSE,
          escape = FALSE) %>%
  formatStyle(columns = 1:ncol(X), fontSize = '90%')
```

# Map {data-icon="ion-android-map"}
## Column 1 {data-width=500, .tabset}
<!-- ### Tiles -->
<!-- ```{r} -->
<!-- # XRAR <- RAR[!asset %in% DT$asset] -->
<!-- map_background <- paste0("https://raw.githubusercontent.com/cnftstats/bossplanet/", -->
<!--                          "main/map_background.png?raw=true") -->


<!-- X <- data.table(expand.grid(x = -180:180, y = -60:180), price_rank = as.numeric(NA)) -->
<!-- X[, xy := paste(x, y, sep = ",")] -->
<!-- setnames(X, c("x", "y"), c("xcoord", "ycoord")) -->

<!-- DT[, xy := paste(xcoord, ycoord, sep = ",")] -->

<!-- loj(X, DT[, .(xcoord, ycoord, price_rank, xy)], "xy") -->

<!-- gg <- ggplot(X) + -->
<!--   geom_tile(aes(xcoord, ycoord, fill = price_rank)) + -->
<!--   scale_x_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) + -->
<!--   scale_y_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) + -->
<!--   labs(color = "Price", x = "", y = "") + -->
<!--   theme(panel.grid.minor = element_blank(), -->
<!--         panel.grid.major = element_line(colour = "grey80"), -->
<!--         panel.background = element_rect(fill = 'transparent')) -->

<!-- ggplotly(gg) %>% config(scrollZoom = TRUE) -->
<!-- ``` -->


### Listings plotly
```{r}
map_background <- paste0("https://raw.githubusercontent.com/cnftstats/bossplanet/",
                         "main/map_background.png?raw=true")

# To do:
# add_polygons (so can be zoomed)

js2 <- "function(el, x) {
    var id = el.getAttribute('id');
    var gd = document.getElementById(id);
    var d3 = Plotly.d3;
    Plotly.update(id).then(attach);
    function attach() {
        gd.addEventListener('mousemove', function(evt) {
            var xaxis = gd._fullLayout.xaxis;
            var yaxis = gd._fullLayout.yaxis;
            var bb = evt.target.getBoundingClientRect();
            var x = xaxis.p2d(evt.clientX - bb.left);
            x = parseFloat(x).toFixed(0);
            var y = yaxis.p2d(evt.clientY - bb.top);
            y = parseFloat(y).toFixed(0);
            var layout_update = {
              annotations: [
                {
                  x: 0,
                  y: -54,
                  xref: 'x',
                  yref: 'y',
                  text: '(' + x + ', ' + y + ')',
                  showarrow: false,
                  font: {
                    size: 14,
                    color: '#b3b3b3',
                  },
                },
              ]
            }
            Plotly.relayout(gd, layout_update);
        });
    };
    el.on('plotly_click', function(d) {
        var link = d.points[0].customdata;
        window.open(link);
    });
}"


X <- copy(DT)

percent_high_low <- 15

.lowest_prices <- DT$price[order(DT$price)]
.lowest_prices <- .lowest_prices[1:(floor(length(.lowest_prices)*percent_high_low/100))]
.lowest_prices <- max(.lowest_prices)

.highest_prices <- DT$price[order(-DT$price)]
.highest_prices <- .highest_prices[1:(floor(length(.highest_prices)*percent_high_low/100))]
.highest_prices <- min(.highest_prices)

X[, show_price := fcase(price <= .lowest_prices, "Low",
                        price > .lowest_prices & price < .highest_prices, "Med",
                        price >= .highest_prices, "High")]
X[, show_price := factor(show_price, levels = c("Low", "Med", "High"))]



plot_ly(
  data = X, x = ~xcoord, y = ~ycoord, split = ~interaction(type, show_price),
  customdata = ~link,
  type = "scatter", mode = "markers",
  text = ~paste0(paste("Price:", price,
                       "</br>District:", district,
                       "</br>Type:", type,
                       "</br>Market:", market)),
  marker = list(
    size = 3,
    color = ~price_rank,
    colorscale = list(c(0, .5, 1), c('#0d71db', "#dbc00d", "#db220d")),
    colorbar = list(
      title = list(text = "Price"),
      len = .5, # length of the color bar
      x = 1,
      y = .25,
      outlinewidth = .5,
      thickness = 15,
      tickmode = "array",
      tickvals = c(0, 1),
      ticktext = c("Low", "High")
    )
    # colorscale = "Jet"
  )
) %>% layout(
  title = "",
  xaxis = list(
    title = list(text = ""),
    range = c(-181, 181),
    tickmode = "array",
    tickvals = c(-180, -60, 60, 180),
    ticktext = c("-180", "-60", "60", "180"),
    color = "#b3b3b3",
    gridcolor = "#cfcfcf",
    layer = "above traces",
    showline = FALSE,
    ticklabelposition = "outside",
    ticklen = 4,
    zeroline = FALSE
  ),
  yaxis = list(
    title = list(text = ""),
    range = c(-61, 181),
    tickmode = "array",
    tickvals = c(-60, 60, 180),
    ticktext = c("-60", "60", "180"),
    color = "#b3b3b3",
    gridcolor = "#cfcfcf",
    layer = "above traces",
    showline = FALSE,
    ticklabelposition = "outside",
    ticklen = 4,
    zeroline = FALSE
    # scaleanchor = "x", # to fix scale ratio so it is square. Pb: makes ticks disapear
    # scaleratio = 1 # to fix scale ratio so it is square. Pb: makes ticks disapear
  ),
  font = list(
    color = "grey",
    size = 12
  ),
  legend = list(
    title = list(text = "Type"),
    x = 1
  ),
  images = list(list(
    source = map_background,
    xref = "x",
    yref = "y",
    x = -183.5,
    y = 181.3,
    sizex = 366.1,
    sizey = 243.7,
    sizing = "stretch",
    opacity = .5,
    layer = "below"
  )),
  margin = list(
    autoexpand = FALSE,
    pad = 0,
    t = 15,
    r = 100,
    b = 30,
    l = 35
  )) %>%
  config(scrollZoom = TRUE, displaylogo = FALSE) %>%
  onRender(js2)
```

### Listings
```{r}
# XRAR <- RAR[!asset %in% DT$asset]
map_background <- paste0("https://raw.githubusercontent.com/cnftstats/bossplanet/",
                         "main/map_background.png?raw=true")

X <- copy(DT)

percent_high_low <- 15

.lowest_prices <- DT$price[order(DT$price)]
.lowest_prices <- .lowest_prices[1:(floor(length(.lowest_prices)*percent_high_low/100))]
.lowest_prices <- max(.lowest_prices)

.highest_prices <- DT$price[order(-DT$price)]
.highest_prices <- .highest_prices[1:(floor(length(.highest_prices)*percent_high_low/100))]
.highest_prices <- min(.highest_prices)

X[, show_price := fcase(price <= .lowest_prices, "Low",
                        price > .lowest_prices & price < .highest_prices, "Med",
                        price >= .highest_prices, "High")]
X[, show_price := factor(show_price, levels = c("Low", "Med", "High"))]

X[, type := factor(type, levels = c("listing", "bundle"), labels = c("Listing", "Bundle"))]

gg <- ggplot() +
  geom_point(data = X, 
             aes(x = xcoord, y = ycoord, color = price_rank, shape = type, customdata = link,
                 alpha = show_price,
                 text = paste0(asset,
                               "</br></br>", paste("Price:", price,
                                                   "</br>District:", district,
                                                   "</br>Type:", type,
                                                   "</br>Market:", market))), size = .6) +
  scale_color_gradient2(low = 'steelblue3', mid = "goldenrod1", midpoint = .5, high = 'red',
                        na.value = "grey90",
                        breaks = 0:1, labels = c("Low", "High"), limits = 0:1) +
  scale_x_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) +
  scale_y_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) +
  scale_shape_manual(name = "Filter", values = c("listing" = 16, "bundle" = 17)) +
  scale_alpha_manual(name = " ", values = rep(1, length(unique(X$show_price)))) +
  labs(color = "Price", x = "", y = "") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_line(colour = "grey80"),
        panel.background = element_rect(fill = 'transparent'),
        legend.title = element_text(size = 11),
        legend.text = element_text(size = 9))
# coord_fixed(xlim = c(-180, 180), ylim = c(-180, 180))


ggplotly(gg, tooltip = "text") %>%
  layout(
    legend = list(x = 1, y = .4, bgcolor = 'rgba(255,255,255,0.6)'),
    images = list(list(
      source = map_background,
      xref = "x",
      yref = "y",
      x = -183.5,
      y = 181.3,
      sizex = 366.1,
      sizey = 243.7,
      sizing = "stretch",
      opacity = .5,
      layer = "below"
    ))
  ) %>%
  config(scrollZoom = TRUE, displaylogo = FALSE) %>% 
  onRender(js) %>% toWebGL()
```

> Click on the data points to open the listings. Zoom-in/out with your mouse wheel. <b><span style='color:red'>Double click on the `(Listing,Low)` legend to display only the lowest listings.</span></b>

### Sales (last 24h)
```{r}
X <- DTS[sold_at_hours <= 24]
X[, sold_time := sprintf("%.fh ago", sold_at_hours)]

gg <- ggplot() +
  # geom_point(data = XRAR, aes(x = xcoord, y = ycoord), color = "grey90", alpha = .9, size = .3) +
  geom_point(data = X, 
             aes(x = xcoord, y = ycoord, color = price_rank,
                 text = paste0(asset,
                               "</br></br>", paste("Price:", price,
                                                   "</br>District:", district,
                                                   "</br>Type:", type,
                                                   "</br>Sold time:", sold_time,
                                                   "</br>Market:", market))), size = .6) +
  scale_color_gradient2(low = 'steelblue3', mid = "goldenrod1", midpoint = .5, high = 'red',
                        na.value = "grey90",
                        breaks = 0:1, labels = c("Lowest", "Highest"), limits = 0:1) +
  scale_x_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) +
  scale_y_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) +
  labs(color = "Price", x = "", y = "") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_line(colour = "grey80"),
        panel.background = element_rect(fill = 'transparent'))
# coord_fixed(xlim = c(-180, 180), ylim = c(-180, 180), expand = TRUE)

ggplotly(gg, tooltip = "text") %>%
  layout(legend = list(x = 1, y = .2, bgcolor = 'rgba(255,255,255,0.6)'),
         images = list(list(
           source = map_background,
           xref = "x",
           yref = "y",
           x = -183.5,
           y = 181.3,
           sizex = 366.1,
           sizey = 243.7,
           sizing = "stretch",
           opacity = .5,
           layer = "below"
         ))) %>%
  config(scrollZoom = TRUE, displaylogo = FALSE) %>% 
  onRender(js) %>% toWebGL()
```

> Click and drag your mouse to zoom. You can zoom-in/out with your mouse wheel. Grey areas are minted lands. I have no clue what the white areas are.

### Plot lands
<iframe src="https://cnftstats.github.io/bossplanet/plot_lands" style="height:100%;width:100%;border:none;" title="plot_lands"></iframe>

### Minted
```{r fig.height=10}
CAP <- RAR[, .(minted = .N, percent = sprintf("%05.02f%%", .N/nrow(RAR)*100)), district]
CAP <- CAP[, sprintf("District %s = %d (%s) lands", district, minted, percent)]
CAP <- paste0(CAP, collapse = "\n")
CAP <- paste0("Total = ", nrow(RAR), " (100%) lands\n", CAP)
cat(CAP)


# ggplot(RAR, aes(x = xcoord, y = ycoord)) +
#   geom_point(color = "grey60", size = .3) +
#   scale_x_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) +
#   scale_y_continuous(breaks = c(-180, -60, +60, +180), expand = c(0.01, 0.01)) +
#   labs(x = "", y = "", title = "Boss Planet minted lands", subtitle = CAP) +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_line(colour = "grey80"),
#         panel.background = element_rect(fill = 'transparent'),
#         plot.title = element_text(color = "firebrick4", size = 15),
#         plot.subtitle = element_text(color = "steelblue3", size = 12)) +
#   coord_fixed(xlim = c(-180, 180), ylim = c(-180, 180), expand = TRUE)
```


# Buy me a coffee {data-icon="ion-coffee"}
## Column 1
### Thanks for your support!
Tips would be greatly appreciated! This would encourage me to maintain and improve the website (for instance, to get a better hosting service).  

![Tip me](tipme.svg){width=200px}  
**addr1qx04gwr9kazlpnm6t8a8h0pggk440zs3fdayct732a0wwwd3usryhnh52pevj5xy7cgp9d4jnywar6g0tnct58dyfukszl25n8** 

# about {.hidden}
## Columun 1
### About the website
#### The data
- Listings data is comes from <a href="https://cnft.io/" target="_blank">cnft.io</a>, <a href="https://www.jpg.store/" target="_blank">jpg.store</a>and <a href="https://www.spacebudz.io/" target="_blank">spacebudz.io</a> marketplaces
- Rank and rarity scores come from <a href="https://cnft.tools/" target="_blank">cnft.tools</a>.
- The website is updated every ~10mins. You need to hit `F5` to manually see the updates on the website.

#### Disclaimer
- This is an early version, so there might be some bugs! Use at your own risk

## Columun 2
### Other useful websites
#### Official websites
- <a href="https://bosscatrocketclub.com/" target="_blank">bosscatrocketclub.com</a>
- <a href="https://chilledkongs.com/" target="_blank">chilledkongs.com</a>
- <a href="https://mocossi.com/" target="_blank">mocossi.com</a>
- <a href="https://spaceapeclub.io/" target="_blank">spaceapeclub.io</a>
- <a href="https://www.pavia.io/" target="_blank">pavia.io</a>

#### General tools
- <a href="https://opencnft.io/" target="_blank">opencnft.io</a>
- <a href="https://cnft.tools/" target="_blank">cnft.tools</a>
- <a href="https://www.cnftjungle.io/" target="_blank">cnftjungle.io</a>
- <a href="https://www.belowfloor.io/" target="_blank">belowfloor.io</a>

#### Specific tools
- <a href="https://pavia.3dkiwi.io/" target="_blank">Pavia heatmap</a>


## Column 3
### About me
- I am passionate about crypto, (c)nfts, stats, and programming!
- Hit me on discord: <a href="https://discord.com/users/K2#8332/" target="_blank">K2#8332</a>
- Follow me on Twitter: <a href="https://twitter.com/cnftstats" target="_blank">@cnftstats</a>


<!-- https://ionic.io/ionicons/v2/cheatsheet.html -->
<!-- https://www.qrcode-monkey.com/#text -->
